\papertitle

### 2014-03-17 final-report/paper.tex
Typo

\system's architecture (Fig.~\ref{fig:arch}) consists of a back-end,
used as a plug-in interface for the distributed database system targeted, and a
front-end which implements the views described above. The front-end and
back-end of \system are highly decoupled so that the visualization can be used not only with
Myria but also with other systems such as Spark or Hadoop. In
Section~\ref{sec:back} we illustrate how we implemented log collections and
aggregation in Myria.

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualziation on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that possible to implement conveniently using D3.

>>>>

\system's architecture (Figure~\ref{fig:arch}) consists of a back-end,
used as a plug-in interface for the distributed database system targeted, and a
front-end which implements the views described above. The front-end and
back-end of \system are highly decoupled so that the visualization can be used not only with
Myria but also with other systems such as Spark or Hadoop. In
Section~\ref{sec:back} we illustrate how we implemented log collections and
aggregation in Myria.

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualization on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that possible to implement conveniently using D3.
